---
title: "ST558Project1"
author: "Shuang Du"
date: "9/4/2020"
output: rmarkdown::github_document
---

# Project 1

## Explaining what you did in the project and any findings you made.

## You should also reflect on the process you went through for this project. Discuss things like:

### What would you do differently in approaching the project?

### what was the most difficult part of the logic and programming for you?

### what are your big take-aways for future projects?

### In your blog post, provide a link to your github pages repo

Repo is <https://github.com/sdu-ncsu/st558project1.git>.
Github pages is address is <https://sdu-ncsu.github.io/st558project1/>

```{r message=FALSE, warning=FALSE}
# devtools::install_github("r-dbi/bigrquery")
library(tidyverse)
library(httr)
library(jsonlite);
library(RSQLite);
```

## Set the libraries needed
```{r}
# global values
base_url_records <- "https://records.nhl.com/site/api"
base_url_stats <- "https://statsapi.web.nhl.com/api/v1/teams"
```


## Create Functions for https://records.nhl.com/site/api
```{r}
# Get all the franchises
getAllFranchises <- function(...) {
  tab_name <- "franchise"
  full_url <- paste0(base_url_records, "/", tab_name)
  
  res <- content(GET(full_url), as="text")
  resR <- fromJSON(res, flatten=TRUE)
  
  return(resR)
}

# Get all the team totals
getTeamTotals <- function(...) {
  tab_name <- "franchise-team-totals"
  full_url <- paste0(base_url_records, "/", tab_name)
  
  res <- content(GET(full_url), as="text")
  resR <- fromJSON(res, flatten=TRUE)
  
  return(resR)
}

# Get franchise season records
getFranchiseSeasonRecords <- function(identifier,...) {

  if (!is.character(identifier) && !is.numeric(identifier)) {
    stop("Invalid identifier type, please specify a character or number")
  }
  
  teamID = identifier
  
  
  tab_name <- "franchise-season-records?cayenneExp=franchiseId="
  full_url <- paste0(base_url_records, "/", tab_name, as.character(teamID))

  res <- content(GET(full_url), as="text")
  resR <- fromJSON(res, flatten=TRUE)

  return(resR)
}

# Get goalie records for a particular team
getGoalieRecords <- function(identifier,...) {

  if (!is.character(identifier) && !is.numeric(identifier)) {
    stop("Invalid identifier type, please specify a character or number")
  }
  teamID = identifier
  
  tab_name <- "franchise-goalie-records?cayenneExp=franchiseId="
  full_url <- paste0(base_url_records, "/", tab_name, as.character(teamID))

  res <- content(GET(full_url), as="text")
  resR <- fromJSON(res, flatten=TRUE)

  return(resR)
}

# Get skater records for particular team
getSkaterRecords <- function(identifier,...) {

  if (!is.character(identifier) && !is.numeric(identifier)) {
    stop("Invalid identifier type, please specify a character or number")
  }
  teamID = identifier
  
  tab_name <- "franchise-skater-records?cayenneExp=franchiseId="
  full_url <- paste0(base_url_records, "/", tab_name, as.character(teamID))

  res <- content(GET(full_url), as="text")
  resR <- fromJSON(res, flatten=TRUE)
  
  return(resR)
}

```

## This function his the endpoint https://statsapi.web.nhl.com/api/v1/teams
### Options (roster, names, previousGame, nextGame, stats, season), teamID, statType, and season encompass the various parameters in the requirements
```{r}
getTeam <- function(options=NULL, teamID=NULL, statType=NULL, season=NULL, ...) {
  
  tab_name <- "?"
  params <- ""
  
  if (!is.vector(options) && !is.null(options)) {
    stop('Options, must be a vector of the following (roster, names, previousGame, nextGame, stats, season)')
  }
  
  if (!is.character(season) && !is.numeric(season) && !is.null(season)) {
    stop("Invalid input type, season must be in the form of two four digit years i.e. 20142015")
  } else if(!is.null(season)) {
    params <- paste0(params, "expand=team.roster&season=",as.character(season),"&")
  }
  
  if (!is.character(statType) && !is.null(statType)) {
    stop("Invalid input type, statType must be a character string")
  } else if (!is.null(statType)) {
    params <- paste0(params, "stats=",statType,"&")
  }
  
  if (!is.character(teamID) && !is.numeric(teamID) && !is.null(teamID)) {
    stop("Invalid input type, teamID must be a numeric value")
  } else if (!is.null(teamID)){
    params <- paste0(params, "teamId=",as.character(teamID),"&")
  }
  
  
  if ('roster' %in% options) {
    params <- paste0(params, "expand=team.roster&")
  }
  if ('names' %in% options) {
    params <- paste0(params, "expand=person.names&")
  }
  if ('nextGame' %in% options) {
    params <- paste0(params, "expand=team.schedule.next&")
  }
  if ('previousGame' %in% options) {
    params <- paste0(params, "expand=team.schedule.previous&") 
  }
  if ('stats' %in% options) {
    params <- paste0(params, "expand=team.stats&")
  }


  full_url <- paste0(base_url_stats, "/", tab_name, params)
    
  res <- content(GET(full_url), as="text")
  resR <- fromJSON(res, flatten=TRUE)
  return(resR)
}
```

## Wrapper function
### Identifier can be either the TeamID or Team Name
### Note that the TeamID is different across the two APIs, so if the same TeamID is used information for different teams will result in the infoType==teamStats and the rest of the infoType options
```{r}
## Wrapper Function


getInfo <- function(infoType, identifier=NULL, options=NULL, statType=NULL, season=NULL, ...) {
  
  if(!(infoType %in% c('franchise', 'teamTotals', 'seasonRecords', 'goalieRecords', 'skaterRecords','teamStats'))) {
    stop('No such api endpoint found, options are: franchise, teamTotals, seasonRecords, goalieRecords, skaterRecords, teamStats')
  }
  
  if(infoType == 'franchise') {
    return(getAllFranchises())
  } else if(infoType == 'teamTotals') {
    return(getTeamTotals())
  } else if(infoType %in% c('seasonRecords', 'goalieRecords', 'skaterRecords')) {
    if (is.character(identifier)) {
      franchiseDF <- getAllFranchises()[[1]]
      subsettedFranchiseTable <- franchiseDF %>% subset(teamCommonName==identifier)
      teamID <- subsettedFranchiseTable$id
      if(length(teamID) == 0) {
        stop("No team found for identifier")
      }
    } else {
      teamID = identifier
    }
    if(infoType == 'seasonRecords') {
      return(getFranchiseSeasonRecords(teamID))  
    } else if(infoType == 'goalieRecords') {
      print(teamID)
      return(getGoalieRecords(teamID)) 
    } else if(infoType == 'skaterRecords') {
      return(getSkaterRecords(teamID))
    }
    
  } else if(infoType == 'teamStats') {
    if (is.character(identifier)) {
      allTeams <- getTeam()
      subsettedTeamsTable <- allTeams[[2]] %>% subset(teamName==identifier)
      teamID <- subsettedTeamsTable$id
      if(length(teamID) == 0) {
        stop("No team found for identifier")
      }
    } else {
      teamID = identifier
    }
    return(getTeam(options=options, teamID=teamID, statType=statType, season=season))
  }
  
}

# getInfo(infoType='seasonRecords', identifier='Maple Leafs')
# getInfo(infoType='teamStats', identifier='Maple Leafs', season=20142015)
# getInfo(infoType='teamStats', identifier=10, season=20142015)

```

## At some point you should do a join on two returned datasets from different API endpoints (say combine them according to franchise ID)

```{r}
allTeams= getInfo(infoType='teamStats')
allTeamsDF <- allTeams$teams %>% rename(franchiseName = name)

MapleLeafGoaliesDF = getInfo(infoType='goalieRecords',identifier='Maple Leafs')$data
RangerGoaliesDF = getInfo(infoType='goalieRecords',identifier='Rangers')$data
RedWingsDF = getInfo(infoType='goalieRecords',identifier='Red Wings')$data

allGoalies = rbind(RangerGoaliesDF, MapleLeafGoaliesDF, RedWingsDF)

joinedAllGoalies <- inner_join(allTeamsDF, allGoalies, by="franchiseName")
```

## You should create at least two new variables
```{r}
joinedAllGoalies <- joinedAllGoalies %>% mutate(mShotsmWinsRatio = mostGoalsAgainstOneGame/mostWinsOneSeason, mostSavesSeasonsRatio = mostSavesOneGame/seasons)
```



```{r}
MapleLeafRecords <- getInfo(infoType='seasonRecords', identifier='Maple Leafs')$data

teamTotals <- getInfo(infoType='teamTotals' )$data
allFranchises <- getInfo(infoType='franchise')$data
```

## You should create some contingency tables

```{r}
table(allTeamsDF$division.abbreviation, allTeamsDF$conference.name)
table(allTeamsDF$venue.timeZone.tz, allTeamsDF$division.nameShort)
```

## You should create numerical summaries for some quantitative variables at each setting of some of your categorical variables

```{r}


reducedGoalies1 <- allGoalies %>% select(franchiseName, mostSavesOneGame)
reducedGoalies2 <- allGoalies %>% select(activePlayer, mostWinsOneSeason)
reducedGoalies3 <- allGoalies %>% mutate('GreaterThanTenSeasons'= case_when(allGoalies$seasons>10 ~ TRUE, allGoalies$seasons <= 10 ~ FALSE)) %>% select(GreaterThanTenSeasons, mostGoalsAgainstOneGame)

mostSavesStats <- reducedGoalies1 %>% group_by(franchiseName) %>%  summarise( 
            n = n(),
            min = fivenum(mostSavesOneGame)[1],
            Q1 = fivenum(mostSavesOneGame)[2],
            median = fivenum(mostSavesOneGame)[3],
            Q3 = fivenum(mostSavesOneGame)[4],
            max = fivenum(mostSavesOneGame)[5]);


mostWinsStats <- reducedGoalies2 %>% group_by(activePlayer) %>%  summarise( 
            n = n(),
            min = fivenum(mostWinsOneSeason)[1],
            Q1 = fivenum(mostWinsOneSeason)[2],
            median = fivenum(mostWinsOneSeason)[3],
            Q3 = fivenum(mostWinsOneSeason)[4],
            max = fivenum(mostWinsOneSeason)[5]);


experienceMostGoalsAgainst <- reducedGoalies3 %>% group_by(GreaterThanTenSeasons) %>%  summarise( 
            n = n(),
            min = fivenum(mostGoalsAgainstOneGame)[1],
            Q1 = fivenum(mostGoalsAgainstOneGame)[2],
            median = fivenum(mostGoalsAgainstOneGame)[3],
            Q3 = fivenum(mostGoalsAgainstOneGame)[4],
            max = fivenum(mostGoalsAgainstOneGame)[5]);


kable(mostSavesStats)
kable(mostWinsStats)
kable(experienceMostGoalsAgainst)
```

## You should create at least five plots utilizing coloring, grouping, etc. All plots should have nice labels and titles.

### You should have at least one bar plot, one histogram, one box plot, and one scatter plot


```{r}
g1 <- ggplot(joinedAllGoalies, aes(x = franchiseName, y = gamesPlayed))
g1 + geom_boxplot(fill = "white") +geom_point(aes(colour=franchiseName), position = "jitter") + ggtitle('Boxplot for Number of Games Played')

g2 <- ggplot(joinedAllGoalies, aes(x=mostGoalsAgainstOneGame))
g2 + geom_histogram(aes(y=..density..),binwidth = .5) + geom_density(lwd=2, adjust=.4, color='red') + ggtitle('Histogram for Most Goals Against') + ylab('Density')

g3 <- ggplot(joinedAllGoalies %>% mutate('activePlayer'= case_when(joinedAllGoalies$activePlayer == TRUE ~ 'Active', joinedAllGoalies$activePlayer == FALSE ~ 'Inactive')), aes(x = activePlayer))
g3 + stat_count() +xlab("Active Players")

g4 <- ggplot(joinedAllGoalies, aes(x = seasons, y = mostShotsAgainstOneGame, colour=franchiseName )) 
g4 + geom_point() + ggtitle('Most Shots Against in a Game')

g5 <- ggplot(joinedAllGoalies, aes(x=mShotsmWinsRatio))
g5 + geom_histogram(aes(y=..density..),binwidth = .19) + ggtitle('Most Shots Against vs Most Wins in One Season Ratio') + facet_wrap(~ franchiseName) + ylab('Density') +xlab('Ratio of Most Shots Against in One Game vs Most Games Won in One Season')

```



